The Astropy Project

### 2017-12-07 main.tex
Apparently join can be a noun

\section{Introduction} \label{sec:intro}
All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Both in packages meant for wider distribution and in scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

@@

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research; e.g., interfacing with
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined the installation
process for many libraries, lowering many barriers to entry.

@@

Tha \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting.
The main motivation for it was creating a framework
which allows arbitrary combination of models to support the Generalized World
Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
The current FITS WCS model lacks the flexibility to represent
arbitrary distortions and does not meet the needs of many types of current instrumentation.
The addition of units to modeling made it attractive for representing
and fitting astrophysical models in various data analysis tools.

Models and fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models, but to also facilitate creating new ones, if necessary.

@@

Models are defined by their parameters and initialized by providing values for them. The
names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
They store additional information -- default value, default unit, and parameter constraints. Parameter
values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
for which the the number of parameters and their names are defined by another argument.
A typical example is a polynomial model defined by its degree.
A model is evaluated by calling it as a function.

If an analytical inverse of a model exists it is already defined and can be
accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
another model which represents a computed inverse.

>>>>

\section{Introduction} \label{sec:intro}
All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

@@

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While the programming language provides support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research; e.g., interfacing with
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages, significantly reducing the entry barrier for using many such libraries.

@@

The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting. Models and
fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models but also make it easy to create new ones if necessary. The
modeling framework is used in a variety of data analysis tools and is the basis
for the Generalized World Coordinate System (GWCS)
package.\footnote{\url{https://github.com/spacetelescope/gwcs}}

@@

Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}. A model is constructed by passing in values (scalars or arrays) for its parameters. A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints. The value and constraints can be updated by assignment. Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values. Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials). Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules. A model is evaluated by calling it as a function.

Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise. This is a settable property; i.e. a model can be assigned as inverse to another model. For example, a polynomial model can be assigned as an inverse to another polynomial model.
